\section*{NeurIPS Paper Checklist}

\begin{enumerate}

\item {\bf Claims}
    \item[] Answer: \answerYes{}
    \item[] Justification: The abstract and introduction clearly state six contributions, all supported by theoretical derivations (Section~2--3) and numerical experiments (Section~4).

\item {\bf Limitations}
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~5.3 discusses limitations: three-body truncation validity, OA accuracy for Gaussian distributions, and the all-to-all coupling assumption.

\item {\bf Theory assumptions and proofs}
    \item[] Answer: \answerYes{}
    \item[] Justification: All theorems and propositions include complete proofs. Key assumptions (Lorentzian distribution, $N\to\infty$ limit, all-to-all coupling) are stated explicitly. Full derivations in Appendices A--B.

\item {\bf Experimental result reproducibility}
    \item[] Answer: \answerYes{}
    \item[] Justification: All simulation parameters (N, $\sigma$, $K_2$/$K_3$ ranges, dt, T, number of trials) are specified in Section~4.1. Code is available in the supplementary repository.

\item {\bf Open access to data and code}
    \item[] Answer: \answerYes{}
    \item[] Justification: All code and data are available at \url{https://github.com/DataLab-atom/code_from_my_agent} (will be anonymized for submission).

\item {\bf Experimental setting/details}
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~4.1 specifies the RK4 integration scheme, time step, total time, parameter grids, and number of random initial conditions for basin probability estimation.

\item {\bf Experiment statistical significance}
    \item[] Answer: \answerNo{}
    \item[] Justification: Error bars are not systematically reported for all experiments. Basin probabilities are estimated from 10--50 trials; the main claims rely on qualitative phase diagram structure rather than precise quantitative values.

\item {\bf Experiments compute resources}
    \item[] Answer: \answerYes{}
    \item[] Justification: Simulations were performed on 8$\times$NVIDIA A800-SXM4-80GB GPUs (640\,GB VRAM total), as stated in Section~4.

\item {\bf Code of ethics}
    \item[] Answer: \answerYes{}
    \item[] Justification: This is foundational research on coupled oscillator theory with no direct ethical concerns.

\item {\bf Broader impacts}
    \item[] Answer: \answerNA{}
    \item[] Justification: This is theoretical/computational physics research on synchronization. Applications to neural and cardiac systems are discussed qualitatively but no deployment is proposed.

\item {\bf Safeguards}
    \item[] Answer: \answerNA{}
    \item[] Justification: No models or datasets with misuse risk are released.

\item {\bf Licenses for existing assets}
    \item[] Answer: \answerNA{}
    \item[] Justification: No pre-existing datasets or pretrained models are used. All code is original.

\item {\bf New assets}
    \item[] Answer: \answerYes{}
    \item[] Justification: We release simulation code and numerical data. The code repository includes documentation and is publicly accessible.

\item {\bf Crowdsourcing and research with human subjects}
    \item[] Answer: \answerNA{}
    \item[] Justification: No human subjects involved.

\item {\bf Institutional review board (IRB) approvals or equivalent for research with human subjects}
    \item[] Answer: \answerNA{}
    \item[] Justification: No human subjects involved.

\item {\bf Declaration of LLM usage}
    \item[] Answer: \answerYes{}
    \item[] Justification: Claude Opus 4.6 was used as a collaborative research tool for mathematical derivations, code generation, and manuscript preparation. Multiple AI agents (GPU-Claude-Opus, HaibiMathAgent, HaibiPlotAnalyst, KuramotoThinker) coordinated via the EACN3 protocol for distributed computation and analysis.

\end{enumerate}
